---
title: "supplementary"
author: "Ehsan"
date: "11/3/2021"
output: html_document
---

**###I wanted to see the age distribution of the participants.**
```{r summarytable,  echo=FALSE}
resulttable=readRDS("../../results/summarytable.rds")
knitr::kable(resulttable, caption = 'Age Percentage of Participants.')
```
_78.9% of total participants are less than or equal  to 35 years old._

**###Next, I wanted to see the gender distribution of the participants**
```{r summarytable2,  echo=FALSE}
resulttable=readRDS("../../results/summarytable2.rds")
knitr::kable(resulttable, caption = 'Sex Percentage of Participants.')
```
_While 45.18% of the participants were female, 54.82% were male._

**###here, I wanted to see which education background each of the participants possessed**
```{r summarytable3,  echo=FALSE}
resulttable=readRDS("../../results/summarytable3.rds")
knitr::kable(resulttable, caption = 'Education Background Percentage of Participants.')
```
_78.05% of the participants had a bachelor or post-bachelor degree_

**###Now, I want to see which income group each of them belong to**
```{r summarytable4,  echo=FALSE}
resulttable=readRDS("../../results/summarytable4.rds")
knitr::kable(resulttable, caption = 'Income Percentage of Participants.')
```
_Almost 50% of the participants belongs to "upper middle income category"_

**###Where do they live?**
```{r summarytable5,  echo=FALSE}
resulttable=readRDS("../../results/summarytable5.rds")
knitr::kable(resulttable, caption = 'Residence Percentage of Participants.')
```
_Less than 10% of the participants live in a village/rural area_

**###Let's see which source they have been using to get updates about covid**
```{r summarytable6,  echo=FALSE}
resulttable=readRDS("../../results/summarytable6.rds")
knitr::kable(resulttable, caption = 'Source of information Percentage of Participants.')
```
_Health professionals and Tv/radio seems to be the most trusted source to the participants._

**###Are most of them working from home or not? Let's find out**
```{r summarytable7,  echo=FALSE}
resulttable=readRDS("../../results/summarytable7.rds")
knitr::kable(resulttable, caption = 'Percentage of Participants working from home or not.')
```
_Apparently equal half of the participants worked from or not_

**###I wanted to see what proportion of the participants had to undergo quarantine at some stages**
```{r summarytable8,  echo=FALSE}
resulttable=readRDS("../../results/summarytable8.rds")
knitr::kable(resulttable, caption = 'Percentage of Participants quarantined or not at some stage.')
```
_Major half of the participants did quarantine at some stage during the study_

**###What proportion of the participants knew their infection status (positive/negative/no test doen)? This is our primary outcome of interest. So, fiinding this was very important**
```{r summarytable9,  echo=FALSE}
resulttable=readRDS("../../results/summarytable9.rds")
knitr::kable(resulttable, caption = 'Percentage of covid test status of the participants.')
```
_63% of the participants didn't go through a COVID test._

**###What was the worry level of the participants? We divided the cohort in groupd like 'moderrately worried', 'a little worried', 'very worried', 'extremely worried' and 'not at all worried'. Proportion for each group is shown below:**
```{r summarytable10,  echo=FALSE}
resulttable=readRDS("../../results/summarytable10.rds")
knitr::kable(resulttable, caption = "Percentage of participants' worry level about (re)infection with COVID-19.")
```
_Almost half of the participants (46%) were moderate or more worried about reinfection_

**###What percent of participants had some sort of chronic disease history? Let's find out**
```{r summarytable11,  echo=FALSE}
resulttable=readRDS("../../results/summarytable11.rds")
knitr::kable(resulttable, caption = "Percentage of participants' history of chronic disease")
```
_Only 22% of the participants recorded to have some sort of chronic disease_


